---
title: "tutorial_postprocessing"
output: html_document
---

First, load the following libraries. (You may need to install them using `install_packages` if you are using this for the first time.) Note that our team has our own [library that we use to pre-define functions used for postprocessing](https://github.com/BershteynLab/EMODAnalyzeR/tree/main/R), so it is an option for you to install and use those functions. Alternatively, you can define your own functions. You are also welcome to contribute to our postprocessing library.

```{r Load Libraries}
library(tidyverse)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
library(readxl)
devtools::install_github("BershteynLab/EMODAnalyzeR")
```

# Read in simulation output
```{r}

res.path.cmd = "/gpfs/scratch/<YOUR_KID>/experiments/"

sim.results <- EMODAnalyzeR::read.simulation.results.bigpurple(
  res.path.cmd,
  scenario_name = 'minimal',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Census year population, for rescaling everything
CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results <- sim.results %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

# Plot Prevalence over time

Read in prevalence calibration target data
```{r}
ingest.file.base = "Data/calibration_ingest_form_Nyanza.xlsm"

obs.prev.sheet.base <- EMODAnalyzeR::read.ingest.sheet(ingest.file.base, "Obs-Prevalence")

obs.prev.sheet.base %>% head
```


```{r, fig.width=8}
#p <- EMODAnalyzeR::emodplot.prevalence(sim.results %>% filter(Age <= 50, Age >=15), 
#                                       1990, 20240)
p <- EMODAnalyzeR::emodplot.prevalence(sim.results %>% filter(Age <= 50, Age >=15), 
                                       1960, 1991)

p +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    ylab("HIV Prevalence (%)") + 
  geom_point(data = obs.prev.sheet.base %>%
               filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
             mapping = aes(x = Year, y = Prevalence)) + 
  geom_errorbar(data = obs.prev.sheet.base %>%
             filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
             mapping = aes(x = Year, ymin = lb, ymax = ub))
```

# Plot Incidence over time

# Plot Mortality over time