---
title: "tutorial_postprocessing"
output: html_document
---

```{r Load Libraries}
library(tidyverse)
library(tidyr)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
library(readxl)
devtools::install_github("BershteynLab/EMODAnalyzeR")
```

# Reading reports

What do reports look like? Let's open a single report and examine it together:

```{r}
res.path = "/gpfs/data/bershteynlab/EMOD/EMOD_tutorial_reports/ReportHIVByAgeAndGender_TPI0001_REP42397.csv"

report.example <- fread(file = res.path)

View(report.example)

```

The formatting and columns of this report are controlled in `config.json`. If there is other information that you want from your simulation, you may need to alter the parameters of `config.json`, or you may need to use a different type of report.

# Read in simulation output
```{r}
res.path = "/gpfs/data/bershteynlab/EMOD/EMOD_tutorial_reports/"

sim.results <- EMODAnalyzeR::read.simulation.results(
  res.path,
  scenario_name = 'tutorial',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed"),
  stratify_columns = c("Year", "Gender", "Age"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

# Census year population, for rescaling everything
CENSUS_YEAR = 2009
KEN_CENSUS_POP = 5352385

sim.results.pop.scaling <- sim.results %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = KEN_CENSUS_POP/total.pop)

sim.results <- sim.results %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

# Plot Prevalence over time

Read in prevalence calibration target data from the ingest file
```{r}
ingest.file.base = "/gpfs/data/bershteynlab/EMOD/<YOUR KID>/tutorial/Data/calibration_ingest_form_Nyanza.xlsm"

obs.prev.sheet.base <- EMODAnalyzeR::read.ingest.sheet(ingest.file.base, "Obs-Prevalence")
```

Calculate prevalence for adults age 15 to 50.
```{r, fig.width=8}
p <- EMODAnalyzeR::emodplot.prevalence(sim.results %>% filter(Age <= 50, Age >=15),
                                      1990, 2040)

p +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,0.25,0.05), limits=c(0, 0.25)) +
    ylab("HIV Prevalence (%)") + 
  geom_point(data = obs.prev.sheet.base %>%
               filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
             mapping = aes(x = Year, y = Prevalence)) + 
  geom_errorbar(data = obs.prev.sheet.base %>%
             filter(Province == 'All', AgeBin == "[15:50)", Gender %in% c("Male", "Female")),
             mapping = aes(x = Year, ymin = lb, ymax = ub))
```

# Plot Mortality over time

This code aggregates together the HIV-related deaths for adults age 15-50
```{r}
hivmort.data <- sim.results %>% 
  filter(Age >= 15, Age < 50) %>% 
  group_by(Year, Gender, sim.id, scenario_name) %>% 
  # note that we need to use the population scaling factor here
  summarize(Died_from_HIV = sum(Died_from_HIV * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup()

```


```{r}
p <- EMODAnalyzeR::emodplot.by_gender(
  hivmort.data,
  date.start = 1990,
  date.end = 2040,
  col2plot = 'Died_from_HIV'
)

p
```


# Suggested activity: ART

Let's practice! Extract ART usage data from the reports and plot it for men and women over time.

# Suggested activity: Discussion

Let's discuss what sorts of research questions you have, and see if we can find ways to address those resesearch questions using EMOD